---
title: "Teens and Tech Exploratory Data Analysis (EDA)"
author: "Jennifer Truong"
date: "2023-08-02"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

# Load packages ----
library(tidyverse)
library(janitor) # for data cleaning
library(here) # for easier file path reading
library(archive) # for interacting with ZIP files

```

```{r Exploring zip files with raw data, include=FALSE}

# Uncomment code lines if doing this for the first time

# Explore structure of raw data ----

# First, let's see what's in the zip files

# This dataset has 5 files
# The one we want is "September 25-October 9, 2014 and February 10-March 6, 2015 - Teens/September 25-October 9, 2014 and February 10-March 6, 2015 - Teens - CSV.csv"

archive(here("raw_data/September-25-October-9-2014-and-February-10-March-6-2015-Teens.zip"))

# This zip file also has 5 datasets
# The one we want is "March 7-April 10, 2018 - Teens and Tech Survey - CSV.csv"

archive(here("raw_data/March-7-April-10-2018-Teens-and-Tech-Survey.zip"))

# Extract CSVs from zip files ----

# archive_extract(here("raw_data/September-25-October-9-2014-and-February-10-March-6-2015-Teens.zip"), dir = here("raw_data"), files = ("September 25-October 9, 2014 and February 10-March 6, 2015 - Teens/September 25-October 9, 2014 and February 10-March 6, 2015 - Teens - CSV.csv"))

# archive_extract(here("raw_data/March-7-April-10-2018-Teens-and-Tech-Survey.zip"), dir = here("raw_data"), files = ("March 7-April 10, 2018 - Teens and Tech Survey - CSV.csv"))

# Extract questionnaire docs from zip files ----

# Could contain metadata for CSVs? 

# archive_extract(here("raw_data/September-25-October-9-2014-and-February-10-March-6-2015-Teens.zip"), dir = here("raw_data"), files = ("September 25-October 9, 2014 and February 10-March 6, 2015 - Teens/September 25-October 9, 2014 and February 10-March 6, 2015 - Teens - Questionnaire.doc"))

# archive_extract(here("raw_data/March-7-April-10-2018-Teens-and-Tech-Survey.zip"), dir = here("raw_data"), files = ("March 7-April 10, 2018 - Teens and Tech Survey - Questionnaire.doc"))

```

## Exploring the data structure

```{r Load CSVs into RStudio}

teens_2014_2015 <- read_csv(here("raw_data/September 25-October 9, 2014 and February 10-March 6, 2015 - Teens/September 25-October 9, 2014 and February 10-March 6, 2015 - Teens - CSV.csv"))

teens_2018 <- read_csv(here("raw_data/March 7-April 10, 2018 - Teens and Tech Survey - CSV.csv"))

```
Dataset | # of Rows | # of Columns
------- | --------- | ------------
2014/5  | 1642      | 50
2018    | 743       | 50

At first glance, these datasets seem very messy. The 2018 dataset seems a lot cleaner though. Even though both datasets have the same number of columns, the columns themselves aren't the same.

- For the 2014-2015 dataset, assume that every column after "xprimelan" is a survey question.
- For the 2018 dataset, assume every column after "surv_lang"  refers to a survey question.

As a side note, this reminded me of what our registration database looked like from the church I worked at as an administrative assistant.

### Survey questions of interest

Let's find questions that relate to owning technology and social media.

Data sources: 

[Pew Research Teens and Tech Survey 2014-15](https://www.pewresearch.org/internet/dataset/september-2014-march-2015-teens/) 

[Pew Research Teens and Tech Survey 2018](https://www.pewresearch.org/internet/dataset/teens-and-tech-survey-2018/)

#### 2014-2015

Primary Key: CaseID

If the answers are letters, each answer is a column and each data point is in binary (usually). These questions also seemed to be answered by parents.

Question | Answers | Definition
-------- | ------- | ---------
P1 | a, b, c, d, e | What tech do you own
P2 | a, b, c, d | Activities on internet
P7 | a, b, c | what social media does the teen use?
P8 | NA | friends with teen on FB?
P9 | NA | follow teen on Twitter?
P10 | NA | connected with teen on social media
P11 | NA | how to contact teen
P12 | a, b, c | know passwords for teen's social media
P13 | a, b, c, d, e | use parental controls to restrict social media
P14 | f, g, h | use parental controls to track activity
P15 | a, b, c, d, e | lecture teens about social media dangers

#### 2018

Primary Key: CASEID

Let's try to find similar questions for the 2018 survey. These questions seemed to be answered by teens.

Question | Answers | Definition
-------- | ------- | ----------
DEVICE   | a, b, c, d | Have or have access to device
INTREQ   | NA | how often does teen use internet
SNS1     | 1, 2, 3, 4, 5, 6, 7, 8 | use any social media website
SNS2     | NA | which social media is used most often
SOC1     | NA | effect of social media on teens

## Key Questions

Seems like I can come up with some key questions.

For the 2014-2015 data:
- What is the relationship between teens' access to devices and using social media?
- How do parents' involvement with their teens' social media affect their usage.

For the 2018 data:
- What is the relationship between teens' access to devices and using social media?
- What is the most used social media platform at the time?
- What is the relationship between teens' social media usage and their effect?

The next step would be to filter the datasets so that they would only contain our columns of interest.

```{r Filter 2014-15 data, echo=FALSE}

teens_1415_filter <- teens_2014_2015 %>% 
  clean_names() %>% 
  select(case_id, p1_a, p1_b, p1_c, p1_d, p1_e,
         p2_a, p2_b, p2_c, p2_d,
         p7_a, p7_b, p7_c,
         p8, p9, p10, p10_1, p11, p11_5,
         p12_a, p12_b, p12_c,
         p13_a, p13_b, p13_c, p13_d, p13_e,
         p14_f, p14_g, p14_h,
         p15_a, p15_b, p15_c, p15_d, p15_e)

# View classes of columns
sapply(teens_1415_filter, class)

# case_id is supposed to be numeric, but I think I know why it's character instead - some of the values are characters instead of numbers
unique(teens_1415_filter$case_id)

# Save value for how many characters should be in case_id instead 
# most IDs range from 1 to 4 characters
str_length(teens_1415_filter$case_id)
max_id_length = 4

# Find rows containing these non-numeric values for case_id 
# There are three records where this is the case
teens_1415_char <- teens_1415_filter %>% 
  filter(str_length(case_id) > max_id_length)

# For the sake of simplicity, we'll remove those rows. This will decrease our sample size from 1642 to 1639, but we should have a sufficent sample size still.
#teens_1415_filter %>% 
  #filter(-(case_id == teens_1415_char$case_id))
```

```{r Filter 2018 data, echo=FALSE}

teens_18_filter <- teens_2018 %>% 
  clean_names() %>% 
  select(caseid, device, devicea, deviceb, devicec, deviced,
         intreq, sns1_1, sns1_2, sns1_3, sns1_4, 
         sns1_5, sns1_6, sns1_7, sns1_8,
         sns2, soc1, soc1a_good_1, soc1a_good_2,
         soc1a_good_3, soc1a_good_4, soc1a_good_5,
         soc1a_good_6, soc1a_good_7, 
         soc1a_bad_1, soc1a_bad_2, soc1a_bad_3, soc1a_bad_4,
         soc1a_bad_5, soc1a_bad_6, soc1a_bad_7, soc1a_dk_ref)

# View classes of columns
sapply(teens_18_filter, class)

```

## Look for missing values

```{r Find missing data for 2014-15 data}
# Load package for missing data
library(naniar)
```

```{r Find missing data for 2018 data}

```

## Look for duplicate values
```{r Find duplicates for 2014-15 data}
# get_dupes()
```

```{r Find duplicates for 2018 data}

```

## Look at data distribution

- Using histogram, box plots, correlation matrices?

```{r View data distribution of 14-15 data}

```

```{r View data distribution of 2018 data}

```

